On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit

### 2023-05-09 manuscript/manuscript.tex
touch up

The standard KS test does not apply to stationary yet dependent data either. The
distribution of the KS statistic would have a higher variance for positively
dependent data than that derived when the data are independent because of a
smaller effective sample size. For example, for testing normality,
\citet{durilleul1992lack} demonstrates that a naive application of
the KS statistic is too liberal for medium-to-high positive serial dependence,
and that for negative dependence, the behavior is asymmetrical. For remedies,
\citet{weiss1978modification} provides a procedure that is applicable 
specifically for data
modeled by the second-order auto-regressive (AR) process where the AR parameters
are known. \citet{lanzante2021testing} tests various strategies for dealing with
temporal
dependence and concludes that a test based on Monte-Carlo simulations performed
the best. When additionally the hypothesized distribution contains unknown
parameters, the standard KS test becomes even further
inapplicable. Practitioners, however, may have used the test without knowing its
limitations \citep[e.g.,][]{tuncer2019online}.

@@

Using the same notations in the text, the nonparametric bootstrap procedure of
\citet{babu2004goodness} is summarized as follows
\citep{babu2004goodness}.
\begin{enumerate}
\item
  Draw a random sample $X_1^*,...,X_n^*$ from the empirical distribution $F_n$
  with replacement.
\item
  Fit $F_\theta$ to $X_1^*,...,X_n^*$ and obtain estimate 
	$\hat\theta_n^*$ of $\theta$.
\item
  Obtain the empirical distribution function $F_n^*$ of
  $X_1^*, \ldots,  X_n^*$. 
\item
  Calculate bootstrap KS statistic
  \[
    D_n^* = \sup_x | \sqrt{n}\left(F_n^* (x)- F_{\hat\theta_n^*}(x)\right) - B_n(x) |.
  \]
  where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known
  bias term \citep{babu2004goodness}.
\item
  Repeat the previous steps a large number $B$ times and use the empirical
  distribution of $D_n^*$ to approximate the null distribution of the observed
  statistic. 
\end{enumerate}
The p-value of $D_n$ is, again, approximated by the proportion of the $D_n^*$
statistics that are greater than or equal to~$D_n$. Note that the step~1 and
step~4 are different from the parametric bootstrap version.

>>>>

The standard KS test does not apply to stationary yet dependent data either. The
distribution of the KS statistic would have a higher variance for positively
dependent data than that derived when the data are independent because of a
smaller effective sample size. For example, for testing normality,
\citet{durilleul1992lack} demonstrates that a naive application of
the KS statistic is too liberal for medium-to-high positive serial dependence,
and that for negative dependence, the behavior is asymmetrical. For remedies,
\citet{weiss1978modification} provides a procedure that is applicable 
specifically for data
modeled by the second-order auto-regressive (AR) process where the AR parameters
are known. \citet{lanzante2021testing} tests various strategies for dealing with
temporal
dependence and concludes that a test based on Monte-Carlo simulations performed
the best. When additionally the hypothesized distribution contains unknown
parameters, the standard KS test becomes even further inapplicable.

@@

Using the same notations in the text, the nonparametric bootstrap procedure 
is summarized as follows \citep{babu2004goodness}.
\begin{enumerate}
\item
  Draw a random sample $X_1^*,...,X_n^*$ from the empirical distribution $F_n$
  with replacement.
\item
  Fit $F_\theta$ to $X_1^*,...,X_n^*$ and obtain estimate 
	$\hat\theta_n^*$ of $\theta$.
\item
  Obtain the empirical distribution function $F_n^*$ of
  $X_1^*, \ldots,  X_n^*$. 
\item
  Calculate bootstrap KS statistic
  \[
    D_n^* = \sup_x | \sqrt{n}\left(F_n^* (x)- F_{\hat\theta_n^*}(x)\right) - B_n(x) |.
  \]
  where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known
  bias term.
\item
  Repeat the previous steps a large number $B$ times and use the empirical
  distribution of $D_n^*$ to approximate the null distribution of the observed
  statistic. 
\end{enumerate}
The p-value of $D_n$ is, again, approximated by the proportion of the $D_n^*$
statistics that are greater than or equal to~$D_n$. Note that the step~1 and
step~4 are different from the parametric bootstrap version.
